Correlation between different emission channels from an atom inside a leaky driven cavity\\ \thanks{corresponding author e-mail: guillermopreisser@hotmail.com}

### 2019-11-19 paper1.2.1.tex
Muchos cambios pablo

%the recent advances?
\section{Introduction}
Spontaneous emission is a phenomenon that has been studied since the
early XX century \cite{10.2307/94746, 1917PhyZ...18..121E}. One of the
main characteristics of spontaneous emission is that
\fxnote{spontaneus emission no es exponencial, es aproximadamente
  exponencial, si quitas la aproximacion markoviana te queda una cola
  polinomial, quite la oracion} the exact time of emission, as well as
the direction in which the photon is emitted, is random, which
difficults its measurement. On the other hand, photons emitted from a
cavity are easy to measure, partly due the fact that we know that they
leave the cavity through one of the lateral mirrors \cite{326305,
  doi:10.1063/1.113345}. The randomness of the direction in which the
photons are emitted by atoms in free space difficults photon counting
experiments. To sort out this difficulty one could think of a physical
arrangement, in which the two-level atom is coupled to the stimulated
mode of a cavity, as it is shown in Fig. \ref{asa} (b). In this
physical arrangement, \fxnote*{tienes una cita donde lo nombren
  asi?}{which is known as the driven Jaynes-Cummings model}, one could
try to estimate the number of spontaneous emissions of the atom
--which are emitted in modes that are not cavity modes and therefore
escape the cavity-- by measuring the photons that leak through one of
the cavity mirrors. In the case that a
correlation exists between the two quantities, we can count the number
of photons that leak the cavity through its mirror, which is easy to
measure, to find information about the number of photons emitted into
the other modes (spontaneus emission), which are difficult to measure.
\begin{center}
\begin{figure*}\label{asa}
\begin{center}
\includegraphics[scale = 0.65]{newimagepaper.pdf}
%\includegraphics[scale = 0.45]{image_paper222.png}
\caption{\small{Physical arrangements of atom and atom in a cavity. In
    both of these arrangements we consider a source which stimulates
    the atom provoking it to spontaneously emit, once it decays. We
    consider a detector in two directions, and we keep a register of
    the number of photons measured in each direction. (a) In the case
    for the atom we don't expect a correlation between m (the number
    of photons measured in the upper side of the atom) and n (the
    number of photons measured in the right side of the atom); (b) for
    the atom in the cavity (a cavity with some loss rate) we study the
    possibility that the cavity generates a correlation between the
    emissions of the atom and the emissions of the cavity, which
    correspond to the emissions that leak through mirror
    2.}} \label{probdisult}
\end{center}
\end{figure*}
\end{center}

@@

\section{Conclusions}\label{sc:conclusions}
Differently to the case of an atom in free space, we can learn
something about the number of spontaneus emissions done by an atom
into different electromagnetic modes if the atom is inside a leaky
cavity.

In this work we considered a driven Jaynes-Cummings system. We made a
program in which, through the use of quantum trajectory theory, we
were able to obtain probability distributions that relate the number
of spontaneous emissions given certain number of cavity emissions.
Through the probability distributions we obtained estimations for the
number of spontaneous emissions by measuring cavity emissions,
considering the correspondent error. Finally we study the existing
correlation where we saw how this correlation decreases as we increase
the cavity linewidth. However, if we try with values for
$\kappa/\gamma < 0.1$, there comes a point where the increase stops
and we see a decrease. We believe this is related to the fact that if
we use enough small values of $\kappa$ there will come a point where
the emission of photons will be too low and this will imply a decrease
in the correlation. The results in this work provide a tool that could
be useful in the manipulation of single photons product of spontaneous
emission, and provide insight into the physical behavior of the driven
Jaynes-Cummings model.

>>>>

%the recent advances?
\section{Introduction}
Spontaneous emission is a phenomenon that has been studied since the
early XX century \cite{10.2307/94746, 1917PhyZ...18..121E}. One of the
main characteristics of spontaneous emission is that
\fxnote{spontaneus emission no es exponencial, es aproximadamente
  exponencial, si quitas la aproximacion markoviana te queda una cola
  polinomial, quite la oracion} the exact time of emission, as well as
the direction in which the photon is emitted, is random, which
difficults its measurement. On the other hand, photons emitted from a
cavity are easy to measure, partly due the fact that we know that they
leave the cavity through one of the lateral mirrors \cite{326305,
  doi:10.1063/1.113345}. The randomness of the direction in which the
photons are emitted by atoms in free space difficults photon counting
experiments. To sort out this difficulty one could think of a physical
arrangement, in which the two-level atom is coupled to the stimulated
mode of a cavity, as it is shown in Fig. \ref{asa} (b). In this
physical arrangement, \fxnote*{tienes una cita donde lo nombren
  asi?}{which is known as the driven Jaynes-Cummings model}, one could
try to estimate the number of spontaneous emissions of the atom
--which are emitted in modes that are not cavity modes and therefore
escape the cavity-- by measuring the photons that leak through one of
the cavity mirrors. In the case that a
correlation exists between the two quantities, we can count the number
of photons that leak the cavity through its mirror, which is easy to
measure, to find information about the number of photons emitted into
the other modes (spontaneus emission), which are difficult to measure.
\begin{center}
\begin{figure*}\label{asa}
\begin{center}
\includegraphics[scale = 0.65]{newimagepaper.pdf}
%\includegraphics[scale = 0.45]{image_paper222.png}
\caption{\small{Physical arrangements of atom and atom in a cavity. In
    both of these arrangements we consider a source which stimulates
    the atom provoking it to spontaneously emit, once it decays. We
    consider a detector in two directions, and we keep a register of
    the number of photons measured in each direction. (a) In the case
    for the atom we don't expect a correlation between m (the number
    of photons measured in the upper side of the atom) and n (the
    number of photons measured in the right side of the atom); (b) for
    the atom in the cavity (a cavity with some loss rate) we study the
    possibility that the cavity generates a correlation between the
    emissions of the atom and the emissions of the cavity, which
    correspond to the emissions that leak through mirror
    2.}} 
\end{center}
\end{figure*}
\end{center}

@@

\section{Conclusions}\label{sc:conclusions}

Atomic emission in cavity and non-cavity modes of an atom inside a
leaky cavity are correlated. The correlations are produced because the
cavity breaks the markovian behavior of atomic emission. the presence
of correlation between photons measured in different directions is a
signature of non-markovian behaviour. This correlation also allows us
to improve the knowledge we know about the probability distribution of
atomic spontaneus emission if we know the number of photons that leak
the cavity.

% In this work we considered a driven Jaynes-Cummings system. We made a
% program in which, through the use of quantum trajectory theory, we
% were able to obtain probability distributions that relate the number
% of spontaneous emissions given certain number of cavity emissions.
% Through the probability distributions we obtained estimations for the
% number of spontaneous emissions by measuring cavity emissions,
% considering the correspondent error. Finally we study the existing
% correlation where we saw how this correlation decreases as we increase
% the cavity linewidth. However, if we try with values for
% $\kappa/\gamma < 0.1$, there comes a point where the increase stops
% and we see a decrease. We believe this is related to the fact that if
% we use enough small values of $\kappa$ there will come a point where
% the emission of photons will be too low and this will imply a decrease
% in the correlation. The results in this work provide a tool that could
% be useful in the manipulation of single photons product of spontaneous
% emission, and provide insight into the physical behavior of the driven
% Jaynes-Cummings model.

\fxnote{Creo que faltan dos cosas en este paper: la correlacion como
  funcion de $g$ dado $\kappa$ constante. Una grafica mostrando, para
  un tiempo fijo, como cambia la funcion de probabilidad para
  emisiones espontaneas como funcion de fotones detectados fuera de la
  cavida. Es decir: $p(n_s,n_c,t_0)$}
